%====================
% EXPERIENCE A
%====================
\subsection{{Doctoral Candidate \hfill SEPT 2019 --- NOV 2025}}
\subtext{Thomas Kislinger Lab, Department of Medical Biophysics, Faculty of Medicine, University of Toronto \hfill Toronto, ON, Canada}
\begin{zitemize}
 \item Evaluated 25 mass spectrometry-based methods for 2 times sample throughput for urine proteomics analysis.
 \item Benchmarked various proteomics computational tools (OpenSWATH, FragPipe, MaxQuant, TPP, DIA-NN, etc.).
\item Automated large-scale analyses in high-performance computing environments (HPCs).
 \item Generated proteomics data from large cohorts of patient samples from pre-analytical sample processing to data curation.
 \item Generated publicly available proteomics databases for data mining purposes.
 \item Collected and curated clinical annotation data from large cohorts of prostate cancer patients.
 \item Evaluated various statistical models for the sensitivity analysis of the best fitting models.
 \item Identified non-invasive markers and biological pathways influenced by ancestry in prostate cancer with statistical analyses on high-dimensional omics data.
\item Performed various supervised and unsupervised analysis on proteomics data to identify associations with cancer outcome.
\item Published scientific manuscripts.
\item Presented research topics at local international conferences.
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{{Researcher \hfill Oct 2017 --- Aug 2019}}
\subtext{Hannes Röst Lab, Donnelly Centre of Cellular and Biological Research \hfill Toronto, ON, Canada}
\begin{zitemize}
    \item Developed scripts for generating proteo-genomics analysis pipelines.
    \item Automated large-scale high-dimensional mass spectrometry data analysis on HPC (slurm) environments.
    \item Evaluated the use of non-model organisms in mass spectrometry-based proteomics analyses.
    \item Optimized novel mass spectrometry method in collaborations with the Bruker Daltonics and Max Planck Institute.
    \item Contributed and modified python packages such as \href{https://pypi.org/project/diapysef/}{\textit{diapysef}} and msproteomicstools for pipeline analysis of novel large proteomics datasets.
    \item Optimized diapysef workflows on various systems (Mac, Linux, Windows) with virtual environments.
    \item Generated detailed workflow tutorials for vendor collaborators.
    \item Documented user tutorial for the \href{https://openswath.org/en/latest/docs/mobidik/mobi-dik.html#}{\textit{MOBI-DIK}} workflows.
    \item Published collaborative scientific manuscript.
    \item Presented research topics at local and international conferences.
\end{zitemize}

%====================
% EXPERIENCE C
%====================
\subsection{{Summer Student \hfill May 2014 --- Aug 2014}}
\subtext{Kai Liu Lab, Hong Kong University of Science and Technology \hfill Hong Kong}
\begin{zitemize}
    \item Dissected and cultured neurons from embryonic mice models to study neurogenic remodeling.
\end{zitemize}

%====================
% EXPERIENCE E
%====================
%\subsection{{ROLE / PROJECT E \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company E \hfill somewhere, state}
%\begin{zitemize}
%    \item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Suspendisse finibus massa eu nisi dictum, a imperdiet tellus convallis.
%    \item Nam feugiat erat vestibulum lacus feugiat, efficitur gravida nunc imperdiet.
%    \item Morbi porta lacus vitae augue luctus, a rhoncus est sagittis.
%\end{zitemize}

%====================
% EXPERIENCE F
%====================
%\subsection{{ROLE / PROJECT F \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company F \hfill somewhere, state}
%\begin{zitemize}
%    \item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%\end{zitemize}

%====================
% EXPERIENCE G
%====================
%\subsection{{ROLE / PROJECT G \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company G \hfill somewhere, state}
%\begin{zitemize}
%    \item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%\end{zitemize}

%====================
% EXPERIENCE H
%====================
%\subsection{{ROLE / PROJECT H \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company H \hfill somewhere, state}
%\begin{zitemize}
%    \item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%\end{zitemize}

%====================
% EXPERIENCE I
%====================
%\subsection{{ROLE / PROJECT I \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company I \hfill somewhere, state}
%\begin{zitemize}
%    \item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%\end{zitemize}